### 2014-03-14 src/analysis.Rnw
update

%\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

>>>>

%\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"
